---
title: "FARS_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FARS_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setenv, echo=FALSE, message=FALSE}
library('farsdata')
library('mapdata')
library('lubridate')
```

This package is primarily built for to check how to build package in R. The package enables one to explore fatal traffic accidents from 2013-2015 using data from the National Highway Traffic Safety Administration (NHTSA) Fatality Analysis Reporting System (FARS). This package is part of assignment of JHU Software development track. 

## The Data

The data in this package come from the National Highway Traffic Safety Administration (NHTSA) Fatality Analysis Reporting System (FARS) data.

```{r sample2013_data}
fars_2013_fn <- make_filename(2013)
fars_2013 <- fars_read(fars_2013_fn) 
dim(fars_2013)
fars_2013
```

For detailed information about the data, see the [NHTSA FARS Manuals & Documentation page]
(https://crashstats.nhtsa.dot.gov/#/DocumentTypeList/4). 

